Supplementary Materials for \\ Modeling the competing effects of the immune system and EMT on epithelial cancers

### 2019-09-23 Paper/Supplement/Supplement_rewrite.tex
updated CleanPaper similarly and put LIHC in Supplement

>>>>

\begin{figure}
\center
{\includegraphics[width=0.65\textwidth]{../Figs/Figure6/LIHC.pdf}}
\caption{A. K-means clustering of LIHC using gene ontology terms indicative of EMT and inflammation signatures ($k=2$).
B. Survival plots corresponding to the clustering on EMT and inflammation.
C. K-means clustering of LIHC using gene ontology terms indicative of an EMT signature ($k=2$).
D. Survival plots corresponding to the clustering on EMT.
E. K-means clustering of LIHC using gene ontology terms indicative of inflammation ($k=2$).
F. Survival plots corresponding to the clustering on inflammation.}
\label{fig:LIHC}
\end{figure}
